---
title: "Oral Methamphetamine Drinking Data Analysis from JCMS for Kumar Lab"
author: "Vivek Kumar"
date: "2023-01-26" # Corrected year and added current date
output:
  html_document:
    df_print: paged
editor_options:
  markdown:
    wrap: 72
---
# GITHUB
https://github.com/vivekJax/JCMS_OM_Suc/ 

# Meth Drinking Data Analysis from JCMS for Kumar Lab

**Author:** Vivek Kumar

**Date:** 2023-01-26 (corrected year and added current date)

## Introduction

This R Notebook analyzes **Drinking of Methamphetamine ** data
from JCMS for the Kumar Lab. The primary objective is to compare and
contrast responses between methamphetamine and sucrose data.

## Downloading Data and Directory Structure
### Notes from Tom
> Column B DataType from all data filter for 'Sucrose' or 'Oral methamphetamine'. 
>
> Last columns AU sort for 'SPT4: 2 day water, 2 days each with increasing dose of sucrose (0.25%, 0.5%, 2%) 2-bottle choice' or AV for 'OM4: 4 days 20mg-L,  4 days 40mg-L,  4 days 80mg-L oral methamphetamine' as needed. 
>
> d1 = body weight (grams), d2 = sucrose or meth water start (grams), d3 = ctrl water start (grams), d4 is sucrose or meth water end (grams), d5 = ctrl water end (grams), d6 = days drank. d13 is a comments field, usually indicating which days are covered by the indicated period since sucrose or meth experiment start (days 1-3, days 3-5, etc.). 
>
> Columns 'Drug', 'DrugDose' and 'DoseUnits' are also needed. Aside from that you just want the usual strain and sex, with MouseID, date, birthDate, Age(wks), etc. being optional.


## Importing Libraries

```{r}
library(stringr)
library(dplyr)
#library(reshape2)
library(ggplot2)
library(readxl)
library(lubridate)
library(data.table)
library(Rmisc)
library(tidyfast)
library(Hmisc)
library(viridis)           
library(ggpubr)
library(rstatix)


################# SET WORKING DIRECTORY
wd <- "/Users/vkumar/Box Sync/LAB/PSY todo/Oral Meth Sucrose Methamphetamine Drinking KOMP/2024_03_March_JCMS_OM_Suc/Data"

setwd(wd)
outputDir <- "../OM_Processed/"

################# READ INPUT FILE 
filename <- "/Users/vkumar/Box Sync/LAB/PSY todo/Oral Meth Sucrose Methamphetamine Drinking KOMP/2024_03_March_JCMS_OM_Suc/Data/MasterData_2024-03-08.xlsx"

# Marina wanted the MouseID to maintain 0 in the front --> upload 012345 which is converted to 12345 with the statement below. It convets MouseID to int
# d1 <- fread(filename, sep = '\t')

# Read and maintain the MouseID as character
# d1 <- fread(filename, sep = '\t', colClasses = c("MouseID" = "character")) # if TSV
# d1 <- fread(filename, sep = ',', colClasses = c("MouseID" = "character")) # if CSV


# Load EXCEL file
# d1 <- as.data.table(read_xlsx(filename, sheet = "TOM_PSYQuery2" )) #made this correction to convert to data.table.
d1 <- as.data.table(read_excel(filename, sheet = "TOM_MasterDataTableQuery", guess_max = 10000), showWarnings = FALSE) #made this correction to convert to data.table.


################# CREATE A FOLDER FOR OUTPUT FILES 
#  Create an empty folder in directory that is one level higher than the input file

 dir.create(file.path("../OM_Processed/"), showWarnings = FALSE)


```





# Filtering Data

**Please note:** You can either uncomment the sucrose filter or leave it
commented out depending on your current analysis focus.

## Future Steps

-   Continue with data cleaning and exploration.
-   Perform desired statistical analyses and visualizations.
-   Document results and interpretations.

**Remember to update instructions and paths as needed.**

I hope this helps!

You should now be able to copy and paste this entire code block into
your R Markdown file editor without any separation issues.

```{r}
# Filter for methamphetamine data only
d1 <- d1[DataType == "Oral methamphetamine"]

# Filter for sucrose data only (uncomment for sucrose analysis)
# d1 <- d1[DataType == "Sucrose"]


```

## Calculating Drug Consumption and Preference

This script aims to calculate different metrics pertaining to drug
consumption and preference based on provided bottle weights and dosing
information. It's designed to work with both Sucrose and Meth data while
acknowledging limitations for Sucrose calculations.

**Data Preparation:**

1.  **Column Renaming:** The script starts by renaming columns from
    their numeric labels to more descriptive names for clarity. These
    changes improve understanding of the data and the calculations
    performed.

2.  **Calculation Columns:**

    -   **Drug/Water Volume Consumed:** We subtract the end weight from
        the start weight of each bottle (drug and water) to estimate the
        volume consumed in grams.
    -   **Drug Preference Score:** This represents the ratio of drug
        volume consumed to the total volume (drug + water). It ranges
        from 0 (only water) to 1 (exclusively drug).

3.  **Drug Consumed per Weight and Day:**

    -   This calculation accounts for animal weight and testing
        duration.
    -   **For Sucrose:** This calculation might not be directly
        meaningful due to its percent weight/volume dosage. While the
        script includes it for consistency, be aware of this limitation.
    -   **For Meth:** The calculation considers the milligram per liter
        dosage and converts it to milligram per gram body weight per
        day.

**Code Breakdown:**

```{r}
# Rename Body Weight Column
colnames(d1)[names(d1) == "d1"] <- "BodyWeight"

# Bottle weights
colnames(d1)[names(d1) == "d2"] <- "DrugBottleStartWeight"
colnames(d1)[names(d1) == "d3"] <- "WaterBottleStartWeight"
colnames(d1)[names(d1) == "d4"] <- "DrugBottleEndWeight"
colnames(d1)[names(d1) == "d5"] <- "WaterBottleEndWeight"

# Length of days between weighing
colnames(d1)[names(d1) == "d6"] <- "MeasureDays"

# Calculate the volume of Drug Water Consumed
# new column for Drug Volume Consumed, units are grams of liquid
d1$DrugVolConsumed <- d1$DrugBottleStartWeight - d1$DrugBottleEndWeight
d1$WaterVolConsumed <- d1$WaterBottleStartWeight - d1$WaterBottleEndWeight

# Calculate Drug Preference
# This is a ratio ranging from 0 to 1
d1$DrugPreferenceScore <- d1$DrugVolConsumed/(d1$DrugVolConsumed + d1$WaterVolConsumed)

# Drug consumed 
# This is normalized for the weight of the animal an dthe number of days the animal is tested
# We calculatet his by multiplying the drug dose by the volume of drug consumed. This is divided by 1000 to correct for liter to ml conversion. This is then divided by the mass of the animal and divided again by the number of days between bottle weighing.
# Note that for Meth the dose is in mg/L. For sucrose it is a percent w/v. 
# We don't really use this number for sucrose. So this is OK. 
# This unit is mg/g BW/day
d1$DrugMassConsumed <- (as.numeric(d1$DrugDose) * d1$DrugVolConsumed/1000)/d1$BodyWeight/d1$MeasureDays
```

## Add test numbers

```{r}
# Making the date correct, if the date is not formatted correctly, adjust this I changed "%m/%d/%Y"
# d1$Date <- ymd(d1$Date) 
d1$Date <- parse_date_time(d1$Date, orders = c('mdy HMS', 'ymd')) #this should handle both formats



################# SORT BY MouseID AND TestDate
d1 <- d1[order(MouseID, Date)]

################# ADD TEST NUMBER AS A NEW COLUMN
d1 <- d1[ , TestNumber := order(Date), by = MouseID]


```

## Determining Animal Count per Dose (Filtered vs. Unfiltered)

This section aims to compare the number of animals across different
doses before and after applying filters.

**Outputs:**

1.  **`d1_Filtered_file.tsv`:** This file contains the filtered `d1`
    data based on specific criteria (dose, tester, strain). Note that
    filtering excludes data based on the number of tests or animals.

    -   **Important:** Duplicated mouse data exists. Utilize tables 2
        and 3 to identify and rectify such instances.

2.  **`StrainFrequencyTable_hasBadData.csv`:** This table presents a
    frequency table for each strain across different drug doses. This
    enables identifying strains lacking sufficient testing (e.g., less
    than 13 tests).

3.  **`Number_tests.csv`:** This table lists the number of tests
    conducted for each individual mouse, grouped by mouse ID and strain.
    It aids in determining missing data for specific animals.

**Reviewing these tables is crucial for ensuring data accuracy.**

**R Code:**

```{r}
# Set working directory (adjust paths as needed)
setwd(wd)
setwd(file.path(outputDir))

# Write filtered d1 data
fwrite(d1, file = "d1_Filtered_file.tsv", sep = "\t")

# Frequency table by strain and dose (identify potential missing data)
freqTable <- dcast(d1, strainName ~ DrugDose, value.var = "DrugDose", fun.aggregate = length)
fwrite(freqTable, "StrainFrequencyTable_hasBadData.csv")

# Table showing number of tests per mouse (identify missing data)
fwrite(d1[, .N, by = .(MouseID, strainName)], file = "Number_tests.csv", sep = ",")

```

#   ------------------------------------------------------------------------------
### Filter and Write Data Excluding "Do Not Use" Entries
### ------------------------------------------------------------------------------
### Purpose:
### - Remove rows containing "Do Not Use" in column d13, indicating unreliable data.
### - Create a new dataset `filtered_data` with the filtered results.
### ------------------------------------------------------------------------------

```{r}
# Specify the text to exclude
excluded_text <- "Do Not Use"

# Filter the data, removing rows with the excluded text
d2 <- d1[!grepl(excluded_text, d13)]

```

#   ------------------------------------------------------------------------------
### Filter Data to remove some non-KOMP strains
### ------------------------------------------------------------------------------
### Purpose:Remove the following strains
### - B6SJL-Tg(5xFAD) HEMI
### - B6SJL-Tg(5xFAD) NCAR
### - C57BL/6J
### - C57BL/6NJ
### - DBA/2J

#   ------------------------------------------------------------------------------
### Fix certain Line Names
### ------------------------------------------------------------------------------
### - Isca had two strains, merging them here

```{r}
# Specify the text to exclude
excluded_strains <- c("B6SJL-Tg(5xFAD) HEMI", "B6SJL-Tg(5xFAD) NCAR", "C57BL/6J", "C57BL/6NJ", "DBA/2J")

# Filter the data, removing rows with the excluded text
d2 <- d2[!strainName %in% excluded_strains, ]

## Fix certain names of line 
d2 <- d2[strainName == 'B6NJ-Isca1tm1a+/- Cyfip2-S968F<J> Hlethal', strainName := 'B6NJ-Isca1']
d2 <- d2[strainName == 'B6NJ-Isca1tm1b+/- Cyfip2-S968F<J> H Lethal', strainName := 'B6NJ-Isca1']

```



```

#   ------------------------------------------------------------------------------
### Filter and Write Data for only the 20,40,80 mg/L
### ------------------------------------------------------------------------------
### Purpose:
### - Remove rows NA for dose, these are the water only days
### - Remove rows 10 for dose, these are the early optimization tests
### - Create a new dataset `filtered_data` with the filtered results.
### - Write the filtered data to a CSV file for further analysis.
### ------------------------------------------------------------------------------

```{r}
# Specify the text to exclude
excluded_dose <- c("10", NA)

# Convert Dose to factor
d2$DrugDose <- as.factor(d2$DrugDose)

# Filter the data, removing rows with the excluded text
d2 <- d2[!DrugDose %in% excluded_dose, ]

# Construct the output file path using clear variable names
output_file_path <- file.path(wd, outputDir, "AnimalsAfterBadTestsRemoved_d2.csv")

# Write the filtered data to the CSV file
write.csv(d2, output_file_path)

# Print a confirmation message with the output file location
print(paste0("Filtered data successfully written to:", output_file_path))

```

# Plotting all lines on one plot, mostly for QC and viewing.

```{r}

setwd(wd)
setwd(file.path(outputDir))

outFileNamePDF <- paste("AllStrainsMAP.pdf", sep = "") ## .. means one directory level up

pdf(outFileNamePDF, 12,12)

#------------------------------------------------------------------------------
#------------------------------------------------------------------------------
p1 <- ggplot(d2, aes(x = as.factor(DrugDose), y = DrugMassConsumed, , fill=DrugDose)) +
      geom_rect(data = subset(d2, strainName == "B6NJ-Cyfip2 S968F<J> (GET204)"), colour = "red", fill = NA, xmin = -Inf,xmax = Inf, ymin = -Inf,ymax = Inf) + 
      geom_boxplot(outlier.shape = NA, color="gray10") +
      geom_point(shape = 1.5, color = "Gray10", position=position_jitter(0.1)) + 
      facet_wrap(~strainName, labeller = labeller(strainName = label_wrap_gen(width = 25))) +
      scale_fill_brewer(palette="Blues") + 
      theme_classic() + 
      labs(title="Oral Methamphetamine consumption (mg Meth per gram BW per day)",x="Dose (mg/L)", y = "mgMeth/gBW/day") +
      theme(legend.position="top")

print(p1)
#------------------------------------------------------------------------------
p1 <- ggplot(d2, aes(x = as.factor(TestNumber), y = DrugMassConsumed, , color=DrugDose, group = c(MouseID))) +
      geom_rect(data = subset(d2, strainName == "B6NJ-Cyfip2 S968F<J> (GET204)"), colour = "red", fill = NA, xmin = -Inf,xmax = Inf, ymin = -Inf,ymax = Inf) + 
      geom_line() +
      geom_point(shape = 1.5) + 
      facet_wrap(~strainName, labeller = labeller(strainName = label_wrap_gen(width = 25))) +
      theme_classic() + 
      labs(title="Oral Methamphetamine consumption (mg Meth per gram BW per day)",x="Dose (mg/L)", y = "mgMeth/gBW/day") +
      theme(legend.position="top")
      
print(p1)
#------------------------------------------------------------------------------

dev.off()

```
# Plot each line compared to the controls
## Box plots with points

```{r}
strainList <- levels(as.factor(d2$strainName))

setwd(wd)
setwd(file.path(outputDir))

outFileNamePDF <- paste("IndividualStrainPlots.pdf") 

pdf(outFileNamePDF, 4,3)

for (toPlot in strainList) {
  # if the strain is control then skip
  if(toPlot=="B6NJ-Cyfip2 S968F<J> (GET204)") next
  # extract the animal to plot
  toPlot1 <- d2[d2$strainName %in% c(toPlot, "B6NJ-Cyfip2 S968F<J> (GET204)"), ]
  
p1 <- ggplot(toPlot1, aes(x = as.factor(DrugDose), y = DrugMassConsumed, , fill=DrugDose)) +
      geom_boxplot(outlier.shape = NA, color="gray10", width = 0.65) +
      facet_wrap(~strainName, labeller = labeller(strainName = label_wrap_gen(width = 25))) +
      scale_fill_brewer(palette="Blues") + 
      theme_classic() + 
      labs(title=stringr::str_wrap(toPlot, width=40), y = "mgMeth/gBW/day") + 
      theme(plot.title = element_text(size = 10, face = "bold")) +
      theme(legend.position="none") + 
      theme(strip.text.x = element_text(size = 8)) # decrease facet font size


      print(p1)
 
  
   p1 <- p1 +
      geom_point(shape = 1.5, color = "Gray10", position=position_jitter(0.1)) 
      
      print(p1)
}

dev.off()

```
# Plot each line compared to the controls facet by sex

```{r}
strainList <- levels(as.factor(d2$strainName))

setwd(wd)
setwd(file.path(outputDir))

outFileNamePDF <- paste("IndividualStrainPlotsSEX.pdf") 

pdf(outFileNamePDF, 4.5,6)

for (toPlot in strainList) {
  # if the strain is control then skip
  if(toPlot=="B6NJ-Cyfip2 S968F<J> (GET204)") next
  # extract the animal to plot
  toPlot1 <- d2[d2$strainName %in% c(toPlot, "B6NJ-Cyfip2 S968F<J> (GET204)"), ]
  
p1 <- ggplot(toPlot1, aes(x = as.factor(DrugDose), y = DrugMassConsumed, , fill=DrugDose)) +
      geom_boxplot(outlier.shape = NA, color="gray10", width = 0.65) +
      facet_grid(sex~strainName, labeller = labeller(strainName = label_wrap_gen(width = 25))) +
      scale_fill_brewer(palette="Blues") + 
      theme_bw() + 
      labs(title=stringr::str_wrap(toPlot, width=40), y = "mgMeth/gBW/day") + 
      theme(plot.title = element_text(size = 10, face = "bold")) +
      theme(legend.position="none") + 
      theme(strip.text.x = element_text(size = 8), # decrease facet font size
            panel.grid.minor = element_blank(),
            panel.grid.major = element_blank()) 
      print(p1)
 
  
   p1 <- p1 +
      geom_point(shape = 1.5, color = "Gray10", position=position_jitter(0.1)) 
      
      print(p1)
}

dev.off()

```
# Plot each animal for each line as a line plot 
## this is to look at consistency of consumption over the doses. 
> summary(d2$DrugMassConsumed)
      Min.    1st Qu.     Median       Mean    3rd Qu.       Max. 
-0.0006316  0.0010975  0.0018353  0.0024572  0.0030947  0.0170526 


```{r}
strainList <- levels(as.factor(d2$strainName))

setwd(wd)
setwd(file.path(outputDir))

outFileNamePDF <- paste("IndividualStrainLineEachDayPlots.pdf") 

pdf(outFileNamePDF, 4,3)

for (toPlot in strainList) {
  toPlot1 <- d2[d2$strainName %in% c(toPlot), ]
  
p1 <- ggplot(toPlot1, aes(x = as.factor(TestNumber), y = DrugMassConsumed, , color=DrugDose, group = c(MouseID))) +          geom_line() + 
      geom_point(shape = 1.5) + 
      theme_classic() + 
      labs(title=labs(title=stringr::str_wrap(toPlot, width=30)),x="Dose (mg/L)", y = "mgMeth/gBW/day") +
      theme(legend.position="top") +
      scale_y_continuous(limits = c(0, max(d2$DrugMassConsumed))) 


print(p1)
 
 }

dev.off()


```

```{r}
#------------------------------------------------------------------------------
# Line Plot
PlotTitle <- ""
xaxisLabel <- "Methamphetamine (mg/L)"
yaxisLabel <- "mgMeth/gBW/day"

#------------------------------------------------------------------------------
# The errorbars overlapped, so use position_dodge to move them horizontally
pd <- position_dodge(0.1) # move them .05 to the left and right

strainList <- levels(as.factor(d2$strainName))

setwd(wd)
setwd(file.path(outputDir))

outFileNamePDF <- paste("IndividualStrainLinePlot_OM.pdf") 

pdf(outFileNamePDF, 4,3)

for (toPlot in strainList) {
  # if the strain is control then skip
  if(toPlot=="B6NJ-Cyfip2 S968F<J> (GET204)") next
  # extract the animal to plot
  toPlot1 <- d2[d2$strainName %in% c(toPlot, "B6NJ-Cyfip2 S968F<J> (GET204)"), ]



p1 <- ggplot(toPlot1, aes(x = as.factor(DrugDose), y = DrugMassConsumed, color = strainName, group = strainName)) +
      geom_linerange(stat = "summary", fun.data = mean_se, position=pd, color = "gray50") +
      stat_summary(fun='mean', geom='point', position=pd, shape = 19) + 
      stat_summary(fun="mean", geom='line', position=pd) +
      graphTheme + 
      labs(title = toPlot, x= xaxisLabel, y = yaxisLabel) +
      theme(legend.position="top") +
      guides(col = guide_legend(nrow = 2)) +
      theme(legend.title=element_blank()) +
      scale_color_brewer(palette = "Dark2") +
      theme(plot.title = element_text(size = 8, face = "bold")) 
print(p1)  

p1 <- p1 + facet_grid(.~ sex)
print(p1)  

}

dev.off()

#------------------------------------------------------------------------------
################ Add significance testing
# https://www.datanovia.com/en/blog/how-to-add-p-values-onto-a-grouped-ggplot-using-the-ggpubr-r-package/


outFileNamePDF <- paste("IndividualStrainLinePlotPvalues_OM.pdf") 

pdf(outFileNamePDF, 4,3)
for (toPlot in strainList) {
      tryCatch({

  # if the strain is control then skip
  if(toPlot=="B6NJ-Cyfip2 S968F<J> (GET204)") next
  # extract the animal to plot
  toPlot1 <- d2[d2$strainName %in% c(toPlot, "B6NJ-Cyfip2 S968F<J> (GET204)"), ]


stat.test <- toPlot1 %>%
  group_by(DrugDose) %>%
  t_test(DrugMassConsumed ~ strainName) %>%
  adjust_pvalue(method = "none") %>%
  add_significance("p.adj")
stat.test


p1 <- ggline(toPlot1, 
             x = "DrugDose", 
             y = "DrugMassConsumed", 
             add = "mean_se", 
             color = "strainName", 
             position=pd, 
             palette = c("#00AFBB", "#E7B800"))
p1 <- p1 + labs(color=NULL) 
p1 <- p1 + guides(col = guide_legend(nrow = 2))

# Add p-values onto the line plots
# Remove brackets using linetype = "blank"
stat.test <- stat.test %>%
  add_xy_position(fun = "mean_se", x = "DrugDose") 

p1 <- p1 + stat_pvalue_manual(
  stat.test,  label = "{p.adj}{p.adj.signif}", 
  tip.length = 0, linetype  = "blank")
  
print(p1)
}, error=function(e){cat("ERROR :",conditionMessage(e), "\n")})

}
dev.off()

#------------------------------------------------------------------------------
################ Add significance testing by sex
# https://www.datanovia.com/en/blog/how-to-add-p-values-onto-a-grouped-ggplot-using-the-ggpubr-r-package/
# https://www.datanovia.com/en/blog/add-p-values-to-ggplot-facets-with-different-scales/


outFileNamePDF <- paste("IndividualStrainLinePlotSexPvalues_OM.pdf") 

pdf(outFileNamePDF, 6,4)
for (toPlot in strainList) {
    tryCatch({
  
  # if the strain is control then skip
  if(toPlot=="B6NJ-Cyfip2 S968F<J> (GET204)") next
  # extract the animal to plot
  toPlot1 <- d2[d2$strainName %in% c(toPlot, "B6NJ-Cyfip2 S968F<J> (GET204)"), ]


stat.test <- toPlot1 %>%
  group_by(DrugDose, sex) %>%
  t_test(DrugMassConsumed ~ strainName) %>%
  adjust_pvalue(method = "none") %>%
  add_significance("p.adj")
stat.test


p1 <- ggline(toPlot1, 
             x = "DrugDose", 
             y = "DrugMassConsumed", 
             add = "mean_se", 
             color = "strainName", 
             position=pd, 
             palette = c("#00AFBB", "#E7B800"),
             facet.by = "sex")
p1 <- p1 + labs(color=NULL) 
p1 <- p1 + guides(col = guide_legend(nrow = 2))

# Add p-values onto the line plots
# Remove brackets using linetype = "blank"
stat.test <- stat.test %>%
  add_xy_position(fun = "mean_se", x = "DrugDose") 

p1 <- p1 + stat_pvalue_manual(stat.test,  label = "{p.adj}{p.adj.signif}", tip.length = 0, linetype  = "blank")

print(p1)

}, error=function(e){cat("ERROR :",conditionMessage(e), "\n")})

}
dev.off()
```



# Check Body Weights Over Tests
> summary(d2$BodyWeight)
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
  12.50   20.60   23.50   23.42   26.20   36.00 
  
### SET range from 15 to 30, it should cover most of the animals

```{r}
strainList <- levels(as.factor(d2$strainName))

setwd(wd)
setwd(file.path(outputDir))

outFileNamePDF <- paste("BodyWeightIndividualStrains.pdf") 

pdf(outFileNamePDF, 6,3)

for (toPlot in strainList) {
  toPlot1 <- d2[d2$strainName %in% c(toPlot), ]
  
p1 <- ggplot(toPlot1, aes(x = as.factor(TestNumber), y = BodyWeight, , color=MouseID, group = MouseID)) +          
      geom_line() + 
      geom_point(shape = 1.5) +   
      theme_classic() + 
      labs(title=stringr::str_wrap(toPlot, width=40), y = "Grams") + 
      theme(legend.position="right") +
      scale_y_continuous(limits = c(15, 35)) +
      guides(col = guide_legend(nrow = 8)) +
      facet_grid(.~sex)

print(p1)
 
 }

dev.off()


# --------------------------------  PLOT ALL MICE ON ONE PLOT
outFileNamePDF <- paste("BodyWeightAllMice.pdf") 

pdf(outFileNamePDF, 12,9)

# fix one datapoint that is too high
# d2[BodyWeight == 266, BodyWeight := 26.6]


p1 <- ggplot(d2, aes(x = as.factor(TestNumber), y = BodyWeight, group = MouseID)) +
      geom_line(aes(color = BodyWeight), alpha = 0.5, linewidth = 0.5) + 
      theme_classic() + 
      labs(title="BW of All OM tests", y = "Grams", x = "Bottle Weight Number") + 
      theme(legend.position="NA") +
      facet_grid(.~sex) +
      scale_color_viridis(option = "D")


print(p1)

dev.off()

```
